---
title: "FinalProject"
author: "Jannelle Legg"
date: "November 15, 2014"
output: html_document
---

```{r}

library(dplyr)
library(tidyr)
library(ggplot2)
library(rgdal)
library(ggmap)

rawData <- read.csv("/Users/JannelleLegg/Clio3/FInalProject/MissionServices.csv", stringsAsFactors = FALSE)
#rawData

cleanedData <- rawData %>%
  tbl_df() %>%
  select(year = Year,
         facility = Facility,
         location = City,
         frequency = Services.Held,
         churchClergy = permanent.clergy,
         CMDMClergy = CMDM.clergy,
         notes = notes)

```

Now that my data is pulled in and organized a bit, need to grab the geocode data using the ggmap library. To do that I need to pull out the city names, create a new frame with the new data and then bind the data back.

```{r}
locations <- cleanedData %>%
  tbl_df() %>%
  select(location)

locations_geocoded <- geocode(locations$location)
#locations_geocoded

locations <- cbind(locations, locations_geocoded)

cleanedData <- cbind(cleanedData, locations_geocoded)

#cleanedData

```

Now I have a chart that provides information on the year, location, frequency (sort of), and clergy for the Church Mission to Deaf-Mutes between 1873 and 1879.

```{r}
write.csv(cleanedData, file="cleanCMDM1.csv", row.names=FALSE)
```

Now to produce the same process on the school data:
```{r}
rawSchools <- read.csv("/Users/JannelleLegg/Clio3/FInalProject/Schools.csv", stringsAsFactors = FALSE)


cleanedSchools <- rawSchools %>%
  tbl_df() %>%
  select(school = School,
         location = Location,
         founded = Year.Founded)

```

```{r}
locationSchools <- cleanedSchools %>%
  tbl_df() %>%
  select(location)

locationSchools_geocoded <- geocode(locationSchools$location)
#locationSchools_geocoded

locationSchools <- cbind(locationSchools, locationSchools_geocoded)

cleanedSchools <- cbind(cleanedSchools, locationSchools_geocoded)

#cleanedSchools
```

```{r}
write.csv(cleanedSchools, file="cleanSchools.csv", row.names=FALSE)
```

